Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-02-24 ms/ms08_figures.tex
ENH egene distance

\begin{figure}[h!]
    %
    \centering
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
    \end{subfigure}
    %
    \caption{} \label{fig:gwas_egene_etisue_per_variant}
    %
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 8: beta and log pval
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure}[!tbp]
%\centering
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{a}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta_neglog10pval.py/eqtl_beta.png}
%\end{subfigure}
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{b}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta_neglog10pval.py/gwas_beta.png}
%\end{subfigure}
%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/eqtl.png}
%\end{subfigure}
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{d}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/gwas.png}
%\end{subfigure}
%
%\caption{eQTL and GWAS effect size/beta (\textbf{a,b}) and eQTL and GWAS significance/p-value (\textbf{c,d}) as a function of the GWAS class count.} \label{fig:beta_pval}
%%Correlation
%\end{figure}

>>>>

\begin{figure}[h!]
    %
    \centering
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/violin.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/violin.png}
    \end{subfigure}
    %
    \caption{} \label{fig:gwas_egene_etisue_per_variant}
    %
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 9: eQTL gene distance
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
    \centering
    %
    \begin{subfigure}[]{.48\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/violin.png}
    \end{subfigure}
    %
    \caption{}
    %
\end{figure}
